Response to Reviewers $Rev^1$

### 2020-04-04 ICT_Frontiers_rev202001.tex
Updates from Overleaf

            Finally, note that the transfer entropy that can be achieved by copying the environment state or the observed part of the environment state is bounded from above by the mutual information between the subsequent environment states or observations. Copying the environment state corresponds to setting $S_{t+1}=E_t$ such that the transfer entropy is
            \begin{align}
             I(S_{t+1}:E_t|S_t)=I(E_t:E_t|E_{t-1})=H(E_t|E_{t-1}).
            \end{align}
            We can represent the part of the environment that we observe by the value of a function applied to the environment state so that

>>>>

            Finally, note that the transfer entropy that can be achieved by copying the environment state or the observed part of the environment state equal to the mutual information between the subsequent environment states or observations. Copying the environment state corresponds to setting $S_{t+1}=E_t$ such that the transfer entropy is
            \begin{align}
             I(S_{t+1}:E_t|S_t)=I(E_t:E_t|E_{t-1})=H(E_t|E_{t-1}).
            \end{align}
            We can represent the part of the environment that we observe by the value of a function applied to the environment state so that in this case we get
            \begin{align}
             I(S_{t+1}:f(E_t)|S_t)=I(f(E_t):f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1}).
            \end{align}
            Now additionally apply a feedforward network with layer $i$ represented by function $g_i$ then we get
            \begin{align}
             I(S_{t+1}: f(E_t)|S_t)=I(g\circ f(E_t):f(E_t)|f(E_{t-1}))=H(f(E_t)|f(E_{t-1}).
            \end{align}

### 2020-04-04 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

        \begin{ans}
            Hi Prof. Hoffman,
            Thank you for your attention to our manuscript and your interesting question. \\
            If we understand correctly, molecular recognition refers to specific types of interactions among molecules to form molecular complexes. There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition. Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness. Therefore, to your question, it is theoretically plausible under the framework of ICT. We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones forming NTIC processes. Nevertheless, with well-defined mathematical definition, this is an empirical and testable question to ICT. We look forward to learning any self-assembly process forming NTIC at molecular scales in the near future.        
        \end{ans}

>>>>

        \begin{ans}
            Hi Prof. Hoffman,
            Thank you for your attention to our manuscript and your interesting question. \\
            If we understand correctly, molecular recognition refers to specific types of interactions among molecules that form molecular complexes. There is no question that molecular complexes are coarse-grainings of molecules via molecular recognition. Based on our hypothesis, if the dynamics of a molecular complex is an NTIC process, the information closure theory of consciousness (ICT) would claim that the molecular complex has a certain degree of consciousness.
            % Therefore, to your question, it is theoretically plausible under the framework of ICT. We speculate that it may be easy to find informationally closed molecular complexes (isolated complexes) but may not be easy to find ones forming NTIC processes. This is an empirical and testable question under the ICT. We look forward to learning any self-assembly process forming NTIC at molecular scales in the near future.        
        \end{ans}
